### 2022-10-14 doc/manuscript/translocation.qmd
Format manuscript, add .csl and .bib files

---
format: docx
editor: visual
csl: science.csl
bibliography: translocation.bib
---

@@

Roland A. Knapp^1,2^\*, Allison Q. Byrne^3,4^, Mark Q. Wilber^5^, Maxwell B. Joseph^6,7^, Thomas C. Smith^1,2^, Andrew P. Rothstein^3,4^, Rob L. Grasso^8^, Erica Bree Rosenblum^3,4^ (exact order to be determined)

@@

^1^Sierra Nevada Aquatic Research Laboratory, University of California; Mammoth Lakes, CA 93546, USA

^2^Earth Research Institute, University of California; Santa Barbara, CA, 93106, USA

^3^Department of Environmental Science, Policy, and Management, University of California; Berkeley, CA 94720, USA

^4^Museum of Vertebrate Zoology, University of California; Berkeley, CA 94720, USA

^5^Department of Forestry, Wildlife, and Fisheries, University of Tennessee Institute of Agriculture; Knoxville, TN 37996, USA

^6^Earth Lab, University of Colorado; Boulder, CO 80303, USA

^7^NCX; San Francisco, CA, XXXXX, USA

^8^Resources Management and Science, Yosemite National Park; El Portal, CA 95318, USA

@@

<!--# No more than 200 words, follow structure described in instructions for authors. 2-3 sentences of basic-level introduction to the field; a brief account of the background and rationale of the work; a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
 and finally, 2-3 sentences putting the main findings into general context so it is clear how the results described in the paper have moved the field forwards. See [annotated example](https://www.nature.com/documents/nature-summary-paragraph.pdf).  -->

### Main

@@

    -   Frogs in the Sierra Nevada: Knapp et al. (2016)

@@

@@

@@

### Competing interests statement

>>>>

---
format: docx
editor: visual
csl: nature.csl
bibliography: translocation.bib
---

@@

Roland A. Knapp^1,2^\*, Allison Q. Byrne^3,4^, Mark Q. Wilber^5^, Maxwell B. Joseph^6,7^, Thomas C. Smith^1,2^, Andrew P. Rothstein^3,4^, Rob L. Grasso^8^, Erica Bree Rosenblum^3,4^

<!--# Exact author order to be determined) -->

@@

^1^Sierra Nevada Aquatic Research Laboratory, University of California, Mammoth Lakes, CA, USA

^2^Earth Research Institute, University of California, Santa Barbara, CA, USA

^3^Department of Environmental Science, Policy, and Management, University of California.
Berkeley, Berkeley, CA, USA

^4^Museum of Vertebrate Zoology, University of California, Berkeley, Berkeley, CA, USA

^5^Department of Forestry, Wildlife, and Fisheries, University of Tennessee Institute of Agriculture, Knoxville, TN, USA

^6^Earth Lab, University of Colorado, Boulder, CO, USA

^7^NCX, San Francisco, CA, USA

^8^Resources Management and Science, Yosemite National Park, El Portal, CA , USA

@@

```{=html}
<!--# No more than 200 words, follow structure described in instructions for authors. 2-3 sentences of basic-level introduction to the field; a brief account of the background and rationale of the work; a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
 and finally, 2-3 sentences putting the main findings into general context so it is clear how the results described in the paper have moved the field forwards. See [annotated example](https://www.nature.com/documents/nature-summary-paragraph.pdf).  -->
```
### Main

@@

    -   Frogs in the Sierra Nevada: Knapp et al. (2016) @knapp2016

@@

::: {#refs}
:::

@@

### Data availability

@@

### Competing interests

The authors declare no competing interests.
